---
title: "Diamonds are Forever"
author: "R Mofidi"
date: "20/07/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, echo=FALSE}
library(ggplot2)
library(plotly)
library(tidyverse)
data("diamonds")
diamonds[1:7]
```

## Diamonds

- Most valuable of Precious Stones
- Valuable assets which increase in Price
- Providence is important
- Diamonds have characteristics such as Size, cut, colour and clarity

#### **Diamond Prices** 

- Are based on the above characteristics
- As well as the Providence of the diamond
- Recorded during the process of certification 
- Re certification: Diamond exchange 
- Considerable cost

## Tidyverse Diamond Data set

Is a large data set of over 50,000 diamonds which is available from  the Tidyverse package. 
It provides 7 variables on 53940 cut diamonds in the US market:

```{r, echo=FALSE}
diamonds[1:7]
head(diamonds,5)
```

Further information is available from: "ggplot2.tidyverse.org/diamonds.html"

## Diamond Price calculations:

- Involve analysis of a multi-dimensional data space 
- Which can be confusing and difficult to interpret

```{r echo=FALSE}
plot_ly(x=diamonds$carat, y=diamonds$depth, z=diamonds$price, type="scatter3d", mode="markers", color = diamonds$cut)
```

## Diamonds are forever "Shiny app"
Our product allows you to price your diamonds in the comfort and safety of your home and have a guide price in order to be able to negotiate a sale. 


Diamonds above US$ 20,000 will will require in person valuation which can be arranged by appointment. Such stones are often traded at auction or in a diamond exchange and are not traded privately


You can preview the Shiny app in the next slide and access it on:
https://reza-mofidi.shinyapps.io/diamonds/ 

## The "shinyApp" (Pun intended)

```{r, echo = FALSE}
library(shiny)

ui <- fluidPage(

    titlePanel("Price My Diamond Dot com "),
    
    sidebarLayout(
        sidebarPanel(
            sliderInput("slidercarat", "What is the weight of the diamond in carats?", 0.55, 4.5, value = 1.1),
            selectInput("cut", "What is the cut?", levels(diamonds$cut)), 
            selectInput("color", "What is the color?", levels(diamonds$color)), 
            selectInput("clarity", "What is the clarity?", levels(diamonds$clarity)), 
        ),
        mainPanel(
            plotOutput("plot1"),
            h4("Predicted Price ($):"),
            h4(textOutput("pred1"))
        )
    )
)


# Define server logic required to draw a histogram
server <- function(input, output) {
        
        model1<- lm(price~0+carat+cut, data = diamonds)
        model2<- lm(price~0+carat, data = diamonds)
        model1pred <- reactive({
            caratInput<- input$slidercarat
            depthInput<- input$sliderDepth
            tableInput<- input$sliderTable
            cutInput<- input$cut
            colorInput<- input$color
            clarityInput<- input$clarity
            
            predict(model1, newdata=data.frame(carat=caratInput, cut=cutInput, color=colorInput, clarity=clarityInput
            ))
            
        })
        
        output$plot1 <- renderPlot({
            caratInput <- input$slidercarat
            
            plot1<- plot(diamonds$carat, diamonds$price, col=diamonds$cut, xlab = "Size in Carat", 
                         ylab = "Price ($)", bty = "n", pch = 16,
                         xlim = c(0.2, 5.01), ylim = c(300, 30000))
            abline(model2, col="blue", cex=1.2)
            points(caratInput, model1pred(), col = "red", pch = 16, cex = 2)
        })
        output$plot2 <- renderPlot({    
            plot2 <- plot_ly(diamonds, x=diamonds$carat, y=diamonds$depth,
                             z=diamonds$price, color = diamonds$cut, type = "scatter3d")
        })
        output$pred1 <- renderText({
            model1pred()
        })
}

# Run the application 
shinyApp(ui = ui, server = server)

```


